Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-08-10 summary.Rmd
minor updates

For these examples, we will set the following parameters:

* $K = 2$
* Mixture parameter $\alpha = .5$
* $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* $\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$

@@

>>>>

For these examples, we set the following parameters:

* Number of underlying clusters $K = 2$
* Mixture parameter $\alpha = .5$
* Within-cluster popularities $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* Between-cluster popularities 
$\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$

@@

For these examples, we set the following parameters:

* Number of underlying clusters $K = 2, 4, 8$
* Mixture parameters $\alpha_k = 1 / K$ for $k = 1, ..., K$
* Within-cluster popularities $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* Between-cluster popularities 
$\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$

```{r clust_err_k, fig.cap = 'IQR of clustering error using Algorithm 2 (red) compared against subspace clustering (blue) for sample sizes from 64 to 2048 and number of clusters from 2 to 8. Simulations were repeated 100 times for each sample size. The $y$-axis is shown on a logarithmic scale.', fig.width = 8}
clustering.df <- readr::read_csv('clustering-k.csv')
clustering.df %>%
  dplyr::group_by(K, n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  scale_y_log10() +
  # scale_x_log10() + 
  labs(y = '1 - adjusted rand index', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'Algorithm 2')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'Algorithm 2')) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC')) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both')
```

```{r lambda_est_k, cache = FALSE, fig.cap = 'Log-log plot of the median and IQR RMSE from Algorithm 4 (red) compared against an MLE-based method (blue) using sample sizes from 64 to 2048 and number of clusters from 2 to 8. Simulations were repeated 100 times for each sample size.', fig.width = 8}
rmse.df <- readr::read_csv('rmse.csv') %>% 
  dplyr::transmute(K = 2,
                   n = n,
                   rmse = rmse,
                   rmse.mle = rmse.mle) %>% 
  dplyr::bind_rows(readr::read_csv('rmse-k.csv'))

rmse.df %>% 
  na.omit() %>% 
  dplyr::group_by(K, n) %>% 
  dplyr::summarise(median.rmse = median(rmse),
                   q1.rmse = quantile(rmse, .25),
                   q3.rmse = quantile(rmse, .75),
                   median.rmse.mle = median(rmse.mle),
                   q1.rmse.mle = quantile(rmse.mle, .25),
                   q3.rmse.mle = quantile(rmse.mle, .75)) %>% 
  dplyr::ungroup() %>% 
  ggplot() + 
  scale_y_log10() + 
  scale_x_log10() +
  geom_line(aes(x = n, y = median.rmse, colour = 'Algorithm 4')) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse, ymax = q3.rmse,
                    colour = 'Algorithm 4')) + 
  geom_line(aes(x = n, y = median.rmse.mle, colour = 'MLE-based')) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse.mle, ymax = q3.rmse.mle,
                   colour = 'MLE-based')) + 
  scale_colour_brewer(palette = 'Set1') + 
  labs(y = 'RMSE', colour = NULL) + 
  facet_wrap(~ K, labeller = 'label_both')
```
